### 2022-09-05 Bloods_LMM.Rmd
tried different model

#Creatine Kinase
```{r}
CKLMM <- lmer(P_CHANGE ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = CK_PCHANGE_CL)
summary(CKLMM)
pairwiseCK <- emmeans(CKLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwiseCK
```
```{r}
tab_model(CKLMM)
```

>>>>

#Creatine Kinase - Percentage Change
```{r}
CKLMM <- lmer(P_CHANGE ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = CK_PCHANGE_CL)
summary(CKLMM)
pairwiseCK <- emmeans(CKLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwiseCK
```
```{r}
tab_model(CKLMM)
```

#Creatine Kinase - Total Change
```{r}
#Cant use total change as the SWBFR is uncharacteristically low
```

```{r}
main_df_noPRE<-main_df2%>%
  filter(!Time_Point %in% "1")
```

```{r}
CKLMM_Total <- lmer(cal_CK ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df_noPRE)
summary(CKLMM_Total)
pairwiseCK_total <- emmeans(CKLMM_Total, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwiseCK_total
```
```{r}
tab_model(CKLMM_Total)
```
